Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-19 Docs/Paper/LaTex/template.tex
Tex Update

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes

@@

\begin{lstlisting}[caption=Code "SMT" using vZ, label=vZ]
1. (declare-const K Int) 
2. (declare-const W Int)
3. (assert (< K 2)) 
4. (assert (< (- W K) 1))
5. (maximize (+ K W)) 
6. (check-sat)
\end{lstlisting}

@@

\textcolor{blue}{The OpenMP is a set of directives that augments the C/C++ and Fortran languages. OpenMP uses the fork-join model of parallel execution}

@@

The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver). Currently, the SMT solvers supported by ESBMC are: Z3 [24], Boolector [25], MathSAT [26], CVC4 [27], and Yices [28]. Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
	\caption{gestaucht}
\end{figure}

@@

OpenMP is a standard Application Programming Interface (API) for shared memory programming, which has been very successful for structural parallelism in applications. The API provides a directive-based programming approach to write parallel versions of C/C++ programs [33]. In OpenMP, the implementation is based on the fork-join model. The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads. After the parallel region finishes (i.e., the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode [7]. Fig. 2 shows our approach called “Multi-core ESBMC”.
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
	\caption{gestaucht}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
	\caption{gestaucht}
	\label{fig2}
\end{figure}

@@

\textcolor{Red}{The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution. As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible. The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
	\caption{gestaucht}
	\label{fig2}
\end{figure}

\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20. When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval. Therefore, there would be 2 new intervals, one from 1 to 9 and another one from 11 to 20, and the returned step would be 10. The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals. }
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
	\caption{gestaucht}
	\label{fig2}
\end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}

@@

\begin{lstlisting}[caption=Code ``{SMT}'' using vZ, label=vZ]
1. (declare-const K Int) 
2. (declare-const W Int)
3. (assert (< K 2)) 
4. (assert (< (- W K) 1))
5. (maximize (+ K W)) 
6. (check-sat)
\end{lstlisting}

@@

\textcolor{red}{The OpenMP is a set of directives for parallel programming that augments the C/C++ and Fortran languages. It supports the most processor architectures and operating systems such as Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows. OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms. OpenMP uses the fork-join model of parallel execution \cite{OpenMP1998}}

\textcolor{red}{The most basic directive of OpenMP is the \#omp pragma parallel for. This directive parallelize the enclosing loop. You can see below an sample of its usage:}

\begin{lstlisting}[caption=OpenMP basic sample]
01.  int i;
02.  #pragma omp parallel for
03.  for (i = 0; i < 10; i++)
04.      a[i] = 2 * i;
\end{lstlisting}

\textcolor{red}{In the example above, the for loop will be execute in parallel. Each iteration of the loop will be execute in a separated thread.}

@@

The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver). Currently, the SMT solvers supported by ESBMC are: Z3 [24], Boolector [25], MathSAT [26], CVC4 [27], and Yices [28]. Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{Image/esbmc-arch-new.pdf} 
	\caption{ESBMC Architecture}
\end{figure}

@@

OpenMP is a standard Application Programming Interface (API) for shared memory programming, which has been very successful for structural parallelism in applications. The API provides a directive-based programming approach to write parallel versions of C/C++ programs [33]. In OpenMP, the implementation is based on the fork-join model. The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads. After the parallel region finishes (i.e., the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode [7]. Fig. 2 shows our approach called “Multi-core ESBMC”.
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
	\caption{ESBMC Multi-core}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
	\caption{ESBMC Multi-core Optimized Sequential Approach}
	\label{fig2}
\end{figure}

@@

\textcolor{Red}{The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution. As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible. The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
	\caption{ESBMC Binary Approach}
	\label{fig2}
\end{figure}

\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20. When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval. Therefore, there would be 2 new intervals, one from 1 to 9 and another one from 11 to 20, and the returned step would be 10. The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals. }
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
	\caption{Binary Step Calculation}
	\label{fig2}
\end{figure}

@@

%35
\bibitem{OpenMP1998}
OpenMP Architecture Review Board, OpenMP C and C++
Application Pogram Interface, Version 1.0, October 1998.
http://www.openmp.org
